---
title: "Narrative Qualtrics Data"
author: "ClaraM"
date: '2023-01-09'
output: html_notebook
---

## IMPORTS
```{r, }
# libraries
library(tidyverse)
library(rio)
library(janitor)
library(csnl)

# raw data
data_numerical <- import("deidentified_narrative_final_choice_numerical.csv")
```


## CLEANING DATA
```{r}
# simplify
data_clean <- data_numerical %>% 
  row_to_names(row_number = 1) %>%          # header as column names
  select(-c(1:22)) %>%                      # getting rid of first 22 columns, metadata
  filter(!row_number() %in% c(1:8))  %>%    # get rid of first 8 lines of codes
  mutate_at(-c(1,152), as.numeric) %>%      # numbers to numeric
  # add_column(reverse = 0) %>%             # adds reverse column; assumes no reverse coding
  filter(!`Please enter your full name` == "" ) %>% filter(!`Please enter your full name` == "Testing")

# hard code remove repeated entries and scheduling column
data_clean <- data_clean[-c(24, 38, 66),]
data_clean <- data_clean[, -255]
```

---
Self questions: demographics(2-6), personality-self(7-36), empathy(37-58), self-esteem(59-94), self-efficacy(95-103), social anxiety(104-113), life satisfaction(114-123), depression(124-151)
Partner questions: relationship length(152), type of relationship(153), closeness(154-155), personality-partner(156-185), PAM(186-199), RCI(200-232), LL(233-245), wire(246-254)
---

## RENAMING COLUMNS
```{r}
## demographic Qs
colnames(data_clean)[1] <- "subject_id"
colnames(data_clean)[2] <- "age"
colnames(data_clean)[3] <- "gender"
colnames(data_clean)[4] <- "sex"
colnames(data_clean)[5] <- "race"
colnames(data_clean)[6] <- "ethnicity"

colnames(data_clean)[152] <- "relationship_length"
colnames(data_clean)[153] <- "relationship_type"


# self Qs
colnames(data_clean)[7:36] <- c("s_bfi_e_s_1", "s_bfi_a_c_2", "s_bfi_c_o_3", "s_bfi_n_a_4", "s_bfi_o_a_5", "s_bfi_e_a_6", "s_bfi_a_r_7", "s_bfi_c_p_8", "s_bfi_n_d_9", "s_bfi_o_i_10", "s_bfi_e_e_11", "s_bfi_a_t_12", "s_bfi_c_r_13", "s_bfi_n_e_14", "s_bfi_o_c_15", "s_bfi_e_s_16", "s_bfi_a_c_17", "s_bfi_c_o_18", "s_bfi_n_a_19", "s_bfi_o_a_20", "s_bfi_e_a_21", "s_bfi_a_r_22", "s_bfi_c_p_23", "s_bfi_n_d_24", "s_bfi_o_i_25", "s_bfi_e_e_26", "s_bfi_a_t_27", "s_bfi_c_r_28", "s_bfi_n_e_29", "s_bfi_o_c_30")
colnames(data_clean)[37:58] <- c(paste0("empathy_", 1:22))
colnames(data_clean)[59:94] <- c(paste0("self_esteem_", 1:36))
colnames(data_clean)[95:103] <- c(paste0("self_efficacy_", 1:9))
colnames(data_clean)[104:113] <- c(paste0("social_anxiety_", 1:10))
colnames(data_clean)[114:123] <- c(paste0("life_satisfaction_", 1:10))
colnames(data_clean)[124:151] <- c(paste0("depression_", 1:28))


# partner Qs
colnames(data_clean)[154:155] <- c(paste0("rrc_", 1:2))
colnames(data_clean)[156:185] <- c("o_bfi_e_s_1", "o_bfi_a_c_2", "o_bfi_c_o_3", "o_bfi_n_a_4", "o_bfi_o_a_5", "o_bfi_e_a_6", "o_bfi_a_r_7", "o_bfi_c_p_8", "o_bfi_n_d_9", "o_bfi_o_i_10", "o_bfi_e_e_11", "o_bfi_a_t_12", "o_bfi_c_r_13", "o_bfi_n_e_14", "o_bfi_o_c_15", "o_bfi_e_s_16", "o_bfi_a_c_17", "o_bfi_c_o_18", "o_bfi_n_a_19", "o_bfi_o_a_20", "o_bfi_e_a_21", "o_bfi_a_r_22", "o_bfi_c_p_23", "o_bfi_n_d_24", "o_bfi_o_i_25", "o_bfi_e_e_26", "o_bfi_a_t_27", "o_bfi_c_r_28", "o_bfi_n_e_29", "o_bfi_o_c_30")
colnames(data_clean)[186:199] <- c(paste0("pam_", 1:14))
colnames(data_clean)[200:225] <- c(paste0("rci_i_", 1:26))
colnames(data_clean)[226:232] <- c(paste0("rci_a_", 1:7))
colnames(data_clean)[233:245] <- c(paste0("ll_", 1:13))
colnames(data_clean)[246:254] <- c("w_k_1", "w_c_2", "w_s_3", "w_k_4", "w_k_5", "w_c_6", "w_s_7", "w_f_8", "w_l_9")
```

### REVERSE CODING COLUMNS
```{r}
# function that reverses values
reverse_code <- function(x) {6-x}

# applying function to assessed columns
data_clean[c('s_bfi_e_s_1', 's_bfi_c_o_3', 's_bfi_a_r_7', 's_bfi_c_p_8', 's_bfi_o_i_10', 's_bfi_n_e_14', 's_bfi_a_c_17', 's_bfi_n_a_19', 's_bfi_o_a_20', 's_bfi_e_a_21', 's_bfi_n_d_24', 's_bfi_e_e_26', 's_bfi_a_t_27', 's_bfi_c_r_28', 's_bfi_o_c_30', 'empathy_3', 'empathy_4', 'empathy_5', 'empathy_7', 'empathy_11', 'empathy_17', 'self_esteem_5', 'self_esteem_6', 'self_esteem_13', 'self_esteem_31', 'life_satisfaction_8', 'o_bfi_e_s_1', 'o_bfi_c_o_3', 'o_bfi_a_r_7', 'o_bfi_c_p_8', 'o_bfi_o_i_10', 'o_bfi_n_e_14', 'o_bfi_a_c_17', 'o_bfi_n_a_19', 'o_bfi_o_a_20', 'o_bfi_e_a_21', 'o_bfi_n_d_24', 'o_bfi_e_e_26', 'o_bfi_a_t_27', 'o_bfi_c_r_28', 'o_bfi_o_c_30', 'pam_6', 'pam_9', 'rci_i_5', 'rci_i_6', 'rci_i_8', 'rci_i_10','rci_i_11', 'rci_i_13', 'rci_i_14', 'rci_i_16', 'rci_i_18', 'rci_i_20', 'rci_i_23', 'rci_i_25')] <- lapply(data_clean[c('s_bfi_e_s_1', 's_bfi_c_o_3', 's_bfi_a_r_7', 's_bfi_c_p_8', 's_bfi_o_i_10', 's_bfi_n_e_14', 's_bfi_a_c_17', 's_bfi_n_a_19', 's_bfi_o_a_20', 's_bfi_e_a_21', 's_bfi_n_d_24', 's_bfi_e_e_26', 's_bfi_a_t_27', 's_bfi_c_r_28', 's_bfi_o_c_30', 'empathy_3', 'empathy_4', 'empathy_5', 'empathy_7', 'empathy_11', 'empathy_17', 'self_esteem_5', 'self_esteem_6', 'self_esteem_13', 'self_esteem_31', 'life_satisfaction_8', 'o_bfi_e_s_1', 'o_bfi_c_o_3', 'o_bfi_a_r_7', 'o_bfi_c_p_8', 'o_bfi_o_i_10', 'o_bfi_n_e_14', 'o_bfi_a_c_17', 'o_bfi_n_a_19', 'o_bfi_o_a_20', 'o_bfi_e_a_21', 'o_bfi_n_d_24', 'o_bfi_e_e_26', 'o_bfi_a_t_27', 'o_bfi_c_r_28', 'o_bfi_o_c_30', 'pam_6', 'pam_9', 'rci_i_5', 'rci_i_6', 'rci_i_8', 'rci_i_10','rci_i_11', 'rci_i_13', 'rci_i_14', 'rci_i_16', 'rci_i_18', 'rci_i_20', 'rci_i_23', 'rci_i_25')], reverse_code)
```

## SUM COLUMNS FOR QUESTIONS
```{r}

### SELF ####

## BFI
# add sum column to be filled 
data_clean <- add_column(data_clean, s_extraversion_sum = 0, s_openness_sum = 0, s_conscientiousness_sum = 0, s_agreeableness_sum = 0, s_neuroticism_sum = 0, .after = "s_bfi_o_c_30")

# fill sum columns with sum of rows of matching columns
data_clean$s_extraversion_sum <- rowSums(select(data_clean, matches("s_bfi_e_")))
data_clean$s_openness_sum <- rowSums(select(data_clean, matches("s_bfi_o_")))
data_clean$s_conscientiousness_sum <- rowSums(select(data_clean, matches("s_bfi_c_")))
data_clean$s_agreeableness_sum <- rowSums(select(data_clean, matches("s_bfi_a_")))
data_clean$s_neuroticism_sum <- rowSums(select(data_clean, matches("s_bfi_n_")))

## OTHER SELF MEASURES
data_clean <- add_column(data_clean, empathy_sum = 0, .after = "empathy_22")
data_clean <- add_column(data_clean, self_esteem_sum = 0, .after = "self_esteem_36")
data_clean <- add_column(data_clean, self_efficacy_sum = 0, .after = "self_efficacy_9")
data_clean <- add_column(data_clean, social_anxiety_sum = 0, .after = "social_anxiety_10")
data_clean <- add_column(data_clean, life_satisfaction_sum = 0, .after = "life_satisfaction_10")
data_clean <- add_column(data_clean, depression_sum = 0, .after = "depression_28")

data_clean$empathy_sum <- rowSums(select(data_clean, matches("empathy_")))
data_clean$self_esteem_sum <- rowSums(select(data_clean, matches("self_esteem_")))
data_clean$self_efficacy_sum <- rowSums(select(data_clean, matches("self_efficacy_")))
data_clean$social_anxiety_sum <- rowSums(select(data_clean, matches("social_anxiety_")))
data_clean$life_satisfaction_sum <- rowSums(select(data_clean, matches("life_satisfaction_")))
data_clean$depression_sum <- rowSums(select(data_clean, matches("depression_")))


### OTHER ###

## RRC
data_clean <- add_column(data_clean, rrc_sum = 0, .after = "rrc_2")
data_clean$rrc_sum <- rowSums(select(data_clean, matches("rrc_")))

## BFI 
data_clean <- add_column(data_clean, o_extraversion_sum = 0, o_openness_sum = 0, o_conscientiousness_sum = 0, o_agreeableness_sum = 0, o_neuroticism_sum = 0, .after = "o_bfi_o_c_30")

data_clean$o_extraversion_sum <- rowSums(select(data_clean, matches("o_bfi_e_")))
data_clean$o_openness_sum <- rowSums(select(data_clean, matches("o_bfi_o_")))
data_clean$o_conscientiousness_sum <- rowSums(select(data_clean, matches("o_bfi_c_")))
data_clean$o_agreeableness_sum <- rowSums(select(data_clean, matches("o_bfi_a_")))
data_clean$o_neuroticism_sum <- rowSums(select(data_clean, matches("o_bfi_n_")))

## PAM
data_clean <- add_column(data_clean, pam_sum = 0, .after = "pam_14")
data_clean$pam_sum <- rowSums(select(data_clean, matches("pam_")))

## RCI
data_clean <- add_column(data_clean, rci_i_sum = 0, .after = "rci_i_26")
data_clean <- add_column(data_clean, rci_a_sum = 0, rci_sum = 0, .after = "rci_a_7")

data_clean$rci_i_sum <- rowSums(select(data_clean, matches("rci_i_")))
data_clean$rci_a_sum <- rowSums(select(data_clean, matches("rci_a_")))
data_clean$rci_sum <- rowSums(select(data_clean, matches("rci_")))

## LL
data_clean <- add_column(data_clean, ll_sum = 0, .after = "ll_13")
data_clean$ll_sum <- rowSums(select(data_clean, matches("ll_")))

## WIRE 
data_clean <- add_column(data_clean, wire_sum = 0, .after = "w_l_9")
data_clean$wire_sum <- rowSums(select(data_clean, matches("w_")))
```

## RELATIONSHIP LENGTH TO NUMERICAL MONTHS
```{r}
# looks for number followed by year/month/week, etc, captures only value
# does not account for : spelled out numbers, misspelled words
yrs_relationship_length <- str_match(data_clean$relationship_length, "([0-9]+(?:\\.[0-9]+)?)\\s*(?i)year[s]?")
months_relationship_length <- str_match(data_clean$relationship_length, "([0-9]+(?:\\.[0-9]+)?)\\s*(?i)month[s]?")
weeks_relationship_length <- str_match(data_clean$relationship_length, "([0-9]+(?:\\.[0-9]+)?)\\s*(?i)week[s]?")

# NAs to 0s for calculations
yrs_relationship_length[is.na(yrs_relationship_length)] <- 0
months_relationship_length[is.na(months_relationship_length)] <- 0
weeks_relationship_length[is.na(weeks_relationship_length)] <- 0

# calculate years and weeks into months, sum
data_clean$relationship_length <- as.numeric(yrs_relationship_length[,2])*12 + as.numeric(months_relationship_length[,2]) + as.numeric(weeks_relationship_length[,2])/4
```

## OUTPUTS
```{r}
# pivots code to long format
data_long <- pivot_longer(data_clean, cols = c(2:ncol(data_clean)), names_to="Questions", values_to = "Values")

# local output
data_clean
data_long

# exporting dataframes for analysis
export(data_long, "NarrativeQualtricsLongData.csv")
export(data_clean, "NarrativeQualtricsData.csv")
```

Graph social relationship questions to get an idea of the variation in types of relationships between dyads
x-> subject id, y -> closeness, color coding by relationship type?? 

subject id to names 
NOT DONE
```{r, fig.width=10, fig.height = 4}
# "1" = "WORK: co-worker", "2" = "WORK: supervisor", "3" = "WORK: subordinate", "4" = "FAMILY: aunt/uncle", "5" = "FAMILY: sibling", "6" = "FAMILY: parent", "7" = "FAMILY: cousin", "8" = "ROMANTIC: married", "9" = "ROMANTIC: engaged", "10" = "ROMANTIC: living together", "11" = "ROMANTIC: exclusive", "12" = "ROMANTIC: non-exclusive", "13" = "FRIENDS: close", "14" = "FRIEND: casual", "15" = "ACQUAINTANCE", "16" = "OTHER"))

closeness_graph <- 
  ggplot(data_clean, mapping = aes(x = subject_id, y = rci_sum, fill = relationship_type)) +
  geom_bar(width = .8, position = "dodge", stat = "identity", na.rm = TRUE) +
  scale_x_discrete(guide = guide_axis(angle = 90)) 

closeness_graph_2 <- 
  ggplot(data_clean, mapping = aes(x = subject_id, y = ll_sum, fill = relationship_type)) +
  geom_bar(width = .8, position = "dodge", stat = "identity", na.rm = TRUE) +
  scale_x_discrete(guide = guide_axis(angle = 90)) 

closeness_graph_3 <- 
  ggplot(data_clean, mapping = aes(x = subject_id, y = pam_sum, fill = relationship_type)) +
  geom_bar(width = .8, position = "dodge", stat = "identity", na.rm = TRUE) +
  scale_x_discrete(guide = guide_axis(angle = 90)) 

closeness_graph
closeness_graph_2
closeness_graph_3
```
```{r}
self_sums <- c("Empathy"=list(data_clean$empathy_sum), "Low Self-Esteem"=list(data_clean$self_esteem_sum), "Self-Efficacy"=list(data_clean$self_efficacy_sum), "Social Anxiety"=list(data_clean$social_anxiety_sum), "Life Satisfaction"=list(data_clean$life_satisfaction_sum), "Depression"=list(data_clean$depression_sum))

# figure out how to get rid of inverse graphs
for (i in 1:length(self_sums)) {
  x_sum <- self_sums[[i]]
  x_name <- names(self_sums[i])

  for (j in 1:length(self_sums)) {
    y_sum <- self_sums[[j]]
    y_name <- names(self_sums[j])
    if (identical(x_sum, y_sum) == FALSE) {
      rcoff <- cor(x_sum,y_sum, use = "complete.obs")
      graph <- ggplot(data_clean, aes(x=x_sum, y=y_sum)) +
      geom_point()  +
      geom_smooth(method=lm) + 
      labs(x = x_name, y = y_name) 
      # annotate(geom="text", x=50, y=50, label=rcoff)
      print(graph)
      print(sprintf("%s vs. %s: R = %.2f, R^2 = %.2f", x_name, y_name, rcoff, rcoff^2))
    
    }
  }
}
```





## SPLITTING QUESTIONS AND ADDING SUM COLUMN
## BAD DON'T USE HAVE TO FIX
# SELF
demographics <- data_clean %>%
  select(1:6) 
demographics

bfi_self <- data_clean %>%
  select(7:36) %>% 
  mutate(total = rowSums(across()))
bfi_self

empathy <- data_clean %>%
  select(37:58) %>% 
  mutate(total = rowSums(across()))
empathy

self_esteem <- data_clean %>%
  select(59:94) %>% 
  mutate(total = rowSums(across()))
self_esteem

self_efficacy <- data_clean %>%
  select(95:103) %>% 
  mutate(total = rowSums(across()))
self_efficacy

social_anxiety <- data_clean %>%
  select(104:113) %>% 
  mutate(total = rowSums(across()))
social_anxiety

life_satisfaction <- data_clean %>%
  select(114:123) %>% 
  mutate(total = rowSums(across()))
life_satisfaction

depression <- data_clean %>%
  select(124:151) %>% 
  mutate(total = rowSums(across()))
depression


# PARTNER
partner <- data_clean %>%
  select(c(1,152:155)) 
partner

relationship_length <- data_clean %>%
  select(152) 
relationship_length

relationship_type <- data_clean %>%
  select(153)
relationship_type

closeness <- data_clean %>%
  select(154,155) %>% 
  mutate(total = rowSums(across()))
closeness

personality_partner <- data_clean %>%
  select(156:185) %>% 
  mutate(total = rowSums(across()))
personality_partner

# personal acquaintance measure ??
PAM <- data_clean %>%
  select(186:199) %>% 
  mutate(total = rowSums(across()))
PAM

# relationship closeness inventory?? 
RCI <- data_clean %>%
  select(200:232) %>% 
  mutate(total = rowSums(across()))
RCI

# loneliness??
LL <- data_clean %>%
  select(233:245) %>% 
  mutate(total = rowSums(across()))
LL

wire <- data_clean %>%
  select(246:253) %>% 
  mutate(total = rowSums(across()))
wire






















